Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-01-20 paper.tex
Visually distinguish Fermi index from coordinate index
Add explanation of background field assumption (3)
Reorder/reword the background field recipe steps

We use the following procedure:
\begin{enumerate}
\item
  Interpolate the equilibrium neutrino chemical potential, $\mu_\nu$,
  from the simulation grid.
\item
  Interpolate $J$ and $G$ from the simulation grid and
  compute the average neutrino energy in the fluid frame
  $\langle \varepsilon \rangle \equiv J/G$.
\item
  Compute the neutrino spectral temperature
  \begin{equation}
    T_\nu = \langle \varepsilon \rangle
    \frac{\mathscr{F}_2(\mu_\nu/T)}{\mathscr{F}_3(\mu_\nu/T)},
  \end{equation}
  where $\mathscr{F}_j$ is the Fermi integral
  \begin{equation}
    \mathscr{F}_j(\eta) = \int_0^\infty dx \, x^j (1+e^{x-\eta})^{-1}.
  \end{equation}
\item
  Assume the background neutrino fields have the same total density
  as the evolved moments
  \begin{align}
    J(\varepsilon) &=
    J \frac{\varepsilon^3}{T_\nu^4 \,\mathscr{F}_3(\mu_\nu/T)}
    (1+\exp(\varepsilon/T_\nu-\mu_\nu/T)^{-1}, \\
    H^\mu(\varepsilon) &=
    H^\mu \frac{\varepsilon^3}{T_\nu^4\, \mathscr{F}_3(\mu_\nu/T)}
    (1+\exp(\varepsilon/T_\nu-\mu_\nu/T)^{-1}.
  \end{align}
\end{enumerate}

>>>>

We use the following procedure:
\begin{enumerate}
\item
  Interpolate the fluid temperature, $T$,
  equilibrium neutrino chemical potential, $\mu_\nu$,
  and evolved neutrino energy and number densities in the fluid frame,
  $J$ and $G$, from the simulation grid.
\item
  Compute the average neutrino energy in the fluid frame
  $\langle \varepsilon \rangle \equiv J/G$.
\item
  Compute the neutrino spectral temperature, assuming equilibrium with the
  fluid
  \begin{equation}
    T_\nu = \langle \varepsilon \rangle
    \frac{\mathscr{F}_2(\mu_\nu/T)}{\mathscr{F}_3(\mu_\nu/T)},
  \end{equation}
  where $\mathscr{F}_b$ is the Fermi integral
  \begin{equation}
    \mathscr{F}_b(\eta) = \int_0^\infty dx \, x^b (1+e^{x-\eta})^{-1}.
  \end{equation}
\item
  Assume the background neutrino fields have the same total density
  as the evolved moments
  \begin{align}
    J(\varepsilon) &=
    J \frac{\varepsilon^3}{T_\nu^4 \,\mathscr{F}_3(\mu_\nu/T)}
    (1+\exp(\varepsilon/T_\nu-\mu_\nu/T)^{-1}, \\
    H^\mu(\varepsilon) &=
    H^\mu \frac{\varepsilon^3}{T_\nu^4\, \mathscr{F}_3(\mu_\nu/T)}
    (1+\exp(\varepsilon/T_\nu-\mu_\nu/T)^{-1}.
  \end{align}
\end{enumerate}
